\ttitle

### 2015-07-04 Chapters/CPET_Survival.tex
CPET_Survival Todos and comments
- The next few commits will be for a new chapter
- Sat out in my camping chair listening to aerosmith

@@

Systemic inflammation has been proposed as one of the intermediary mechanism in these patients that increases rates of recurrence and decreases disease free survival. The modified Glasgow Prognostic Score, a measure of preoperative systemic inflammation in cancer patients, is associated with poor survival regardless of the site or stage of cancer. This is discussed in detail in Section \ref{sec:intro_systemic_inflammation_outcome}
.

@@

%UNIVARIATE Cox-regression analysis
The clinico-pathological characteristics of the patients studied (n=47) are shown in Table \ref{table:cpet_survival_cox} on p\pageref{table:cpet_survival_cox}.   The median age of the patients was 66 years (IQR 57 - 70 years).

@@

Kaplan-Meier survival analysis comparing survival in patients with a low ($leq14$) versus high ($>14$) POSSUM Phsyiology Score is shown in Fig. \ref{fig:cpet_survival_km_possum}. Estimated median survival was  32 months (95\% CI 17.02 - 46.99) in patients with a low POSSUM Physiology Score but reduced to 14 months (95\% CI 9.51 - 18.49) in a high POSSUM Physiology Score (p = 0.012).

@@

The results of the present

>>>>

\todo{Should complications-survival also be included in this chapter?}

@@

Systemic inflammation has been proposed as one of the intermediary mechanism in these patients that increases rates of recurrence and decreases disease free survival. The modified Glasgow Prognostic Score, a measure of preoperative systemic inflammation in cancer patients, is associated with poor survival regardless of the site or stage of cancer. This is discussed in detail in Section \ref{sec:intro_systemic_inflammation_outcome}.

@@

%UNIVARIATE Cox-regression analysis
The clinico-pathological characteristics of the patients studied (n=47) are shown in Table \ref{table:cpet_survival_cox} on p\pageref{table:cpet_survival_cox}.   The median age of the patients was 66 years (Inter-Quartile Range, IQR 57 - 70 years).

@@

Kaplan-Meier survival analysis comparing survival in patients with a low ($leq14$) versus high ($>14$) POSSUM Phsyiology Score is shown in Fig. \ref{fig:cpet_survival_km_possum}. Estimated median survival was  32 months (95\% CI 17.02 - 46.99) in patients with a low POSSUM Physiology Score but reduced to 14 months (95\% CI 9.51 - 18.49) in patients with a high POSSUM Physiology Score (p = 0.012).

@@

The results of the present study suggest that comorbidity as measured by the POSSUM Physiology Score may be associated with shorter long-term survival in patients with pancreatic ductal adenocarcinoma.

%Lack of assocation with CPET

%Tumour factors trump comorbidity

Overall median survival in this study was [\todo{pending result}? months] which is considerably shorter than that reported in other studies on the impact of comorbidty on long-term survival. The short median survival is a consequence of the aggressive nature of pancreatic ductal adenocarcinoma and is similar to previously published literature. [\todo{pending reference}] This is also demonstrated in Table \ref{table:cpet_survival_cox_tumour_factors}. This

%Discuss limitations
% - Small numbers
% - Selection bias - patients with significant comorbidity would have not been offered surgery
% - No information on adjuvant therapy

There are several limitations to this study. The number of patients included in this study is small (47) which increases the risk of a Type 2 error. Patients with resectable disease who underwent surgery were by definition a fitter cohort with fewer comorbdities. This introduces a selection bias and may have affected the results. The impact of adjuvant therapy
